---
title: "SummaryEDA"
author: "Joseph Fader"
date: "9/2018"
output: html_document
---

####libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(feather)
library(grid)
``` 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

####load data
```{r}
sets_deep_all <- read_feather("Data/sets_deep_all.feather")
```

#### Interaction summary, all years -- some rates and terminology from Rabearisoa 2018
```{r}

sets_deep_all %>%
       summarise(
         totalsets = n(),
         totalhooks = sum(NUM_HKS_SET),
         CPUE_all = sum(FISH) / totalhooks * 1000, # note does not include any sharks
         CPUE_K = sum(KEPT) / totalhooks * 1000, # should be comparable to LPUE below?
         DP_MM_sets = sum(as.numeric(as.character(MM_YN)), na.rm = T),
         DP_MM_sets = sum(ifelse(MM_sum >=1, 1, 0), na.rm = T),
         DP_MM_tot = sum(MM_sum, na.rm = T),
         MM_any = sum(as.numeric(as.character(MM_any)), na.rm = T),
         nonMM_sets = totalsets - DP_MM_sets,
         FKW_sets = sum(ifelse(FKW_sum >= 1, 1, 0), na.rm = T),
         FKW_total = sum(FKW_sum, na.rm = T),
         IR_MM_DP = DP_MM_sets / totalsets,
         IR_MM_any = MM_any / totalsets,
         DPUE = sum(DP_MM_tot) / totalhooks * 1000,
         DPrate = DP_MM_sets / totalsets,
         FKWrate = FKW_sets / totalsets,
         Rissos = sum(ifelse(RISS_sum >= 1, 1, 0), na.rm = T),
         GDR_MM = DP_MM_tot / sum(FISH)
       ) %>%
  knitr::kable()

## by depredation or not
sets_deep_all %>%
  #filter(MM_YN == 1) %>% 
  group_by(MM_YN) %>%
  #group_by(YEAR) %>%
    summarise(
         totalsets = n(),
         totalhooks = sum(NUM_HKS_SET),
         CPUE_all = sum(FISH) / totalhooks * 1000, # note does not include any sharks
         CPUE_K = sum(KEPT) / totalhooks * 1000, # should be comparable to LPUE below?
         DP_MM_sets = sum(ifelse(MM_sum >=1, 1, 0), na.rm = T),
         DP_MM_tot = sum(MM_sum, na.rm = T),
         FKW_sets = sum(ifelse(FKW_sum >= 1, 1, 0), na.rm = T),
         FKW_total = sum(FKW_sum, na.rm = T),
         DPUE = sum(DP_MM_tot) / totalhooks * 1000,
         LPUE = CPUE_all - DPUE,
         DR_1 = DP_MM_tot / sum(FISH),
         DR_2 = DP_MM_tot / sum(KEPT),
         DR_3 = DPUE / CPUE_all,
         DR_4 = (CPUE_all - LPUE) / CPUE_all
       ) %>%
  knitr::kable()
```

#### damage
```{r}

## sets with both depredation and FKW caught vs one or the other
sets_deep_all %>% 
  summarise(
    sum(MM_sum >= 1 & FKW_sum >= 1),
    sum(MM_sum >= 1 | FKW_sum >= 1),
    sum(FKW_sum >=1)
  )
  knitr::kable()

```

## Time and space

### Soak
#The max soak is `r max(sets_deep_all$SOAK)*60` minutes and `r max(sets_deep_all$SOAK)` hours  
#The min soak is `r min(sets_deep_all$SOAK)*60` minutes and `r min(sets_deep_all$SOAK)` hours

## Soak Time
```{r echo=FALSE}

## histogram
ggplot(data = sets_deep_all) +
  geom_histogram(mapping = aes(x = as.numeric(SOAK)), binwidth = 0.05) + xlab("Histo soak all areas (hours)")
sets_deep_all %>% 
  filter(SOAK < 40) %>% 
  ggplot() +
  geom_histogram(mapping = aes(x = as.numeric(SOAK)), binwidth = 0.05) + xlab("Histo soak all areas (hours)")

# depredation occurrence
sets_deep_all %>% drop_na(MM_YN) %>%
  ggplot(mapping = aes(x = as.numeric(SOAK), y = ..density.., colour = as.factor(MM_YN))) +
  geom_freqpoly(binwidth = 0.3) + xlab("freq of soak by MM occurrence (hours)")
sets_deep_all %>% drop_na(MM_YN) %>% 
  ggplot(mapping = aes(x = as.factor(MM_YN), y = as.numeric(SOAK))) +
  geom_boxplot() + xlab("MM occurence yes or no")
```

## Number of Hooks
```{r echo=FALSE}

## histogram - all hooks
ggplot(data = sets_deep_all) +
  geom_histogram(mapping = aes(x = NUM_HKS_SET), binwidth = 100) + xlab("Histo all hooks")

# depredation occurrence
sets_deep_all %>% drop_na(MM_YN) %>%
  ggplot(mapping = aes(x = NUM_HKS_SET, y = ..density.., colour = as.factor(MM_YN))) +
  geom_freqpoly(binwidth = 300 )

```


## Lag dist
```{r echo=FALSE}

# histogram - all lag
ggplot(data = sets_deep_all) +
  geom_histogram(mapping = aes(x = LAG_DIST), binwidth = 10) + xlab("Histo all hooks")

# depredation occurrence

sets_deep_all %>% drop_na(MM_any) %>% filter(DP_LAG1 == 1) %>%
  ggplot(mapping = aes(x = LAG_DIST, y = ..density.., colour = as.factor(MM_any))) +
  geom_freqpoly(binwidth = 20 ) + xlab("MM occurrence following DP or FKW by distance")
sets_deep_all %>% filter(DP_LAG1 == 1) %>%
  ggplot(mapping = aes(x = as.factor(MM_any), y = LAG_DIST)) +
  geom_boxplot() + xlab("MM occurence yes or no")

sets_deep_all %>% drop_na(MM_any) %>%
  ggplot(mapping = aes(x = LAG_DIST, y = ..density.., colour = as.factor(DP_LAG1))) +
  geom_freqpoly(binwidth = 20 ) + xlab("Distance moved following MM vs nonMM set")
```




### Lag time
```{r echo=FALSE}
# depredation occurrence
sets_deep_all %>% drop_na(MM_YN) %>% filter(DP_LAG1 == 1) %>%
  ggplot(mapping = aes(x = SET_LAG, y = ..density.., colour = as.factor(MM_YN))) +
  geom_freqpoly(binwidth = 1 ) + xlab("lag time by MM occurrence")
sets_deep_all %>% drop_na(MM_YN) %>% filter(DP_LAG1 == 1) %>%
  ggplot(mapping = aes(x = as.factor(MM_YN), y = SET_LAG)) +
  geom_boxplot() + xlab("MM occurence yes or no")

```



## depth - possible difference?
```{r echo=FALSE}
sets_deep_all %>% drop_na(MM_YN) %>%
  ggplot(mapping = aes(x = MIN_LEN, y = ..density.., colour = as.factor(MM_YN))) +
  geom_freqpoly(binwidth = 2 )

```


### more MM plots
```{r echo=FALSE}
# depredation occurrence

## latitude
sets_deep_all %>% drop_na(MM_YN) %>% 
  ggplot(mapping = aes(x = SET_BEGIN_LAT, y = ..density.., colour = as.factor(MM_YN))) +
  geom_freqpoly(binwidth = 0.5 )
## light sticks
sets_deep_all %>% drop_na(MM_YN) %>% 
  ggplot(mapping = aes(x = NUM_LITE_DEVICES, y = ..density.., colour = as.factor(MM_YN))) +
  geom_freqpoly(binwidth = 50 )
## hooks bt floats - no apparent difference
sets_deep_all %>% drop_na(MM_YN) %>% 
  ggplot(mapping = aes(x = HKS_PER_FLT, y = ..density.., colour = as.factor(MM_YN))) +
  geom_freqpoly(binwidth = 2 )

```



